\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ferdinand Hubbard} % Your name
\address{+32 479 820 811 \\ Brussels, Belgium} 
\address{\href{mailto:ferdinandhubbard@gmail.com}{ferdinandhubbard@gmail.com} \\ 
\href{https://www.linkedin.com/in/ferdinand-hubbard/}{linkedin.com/in/ferdinand-hubbard} \\
\href{https://github.com/ferdinandhubbard981}{github.com/ferdinandhubbard981}}

\begin{document}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------


Motivated and skilled software engineer with a strong academic foundation in computer science and practical experience in software development. A bilingual professional passionate about leveraging technology to solve real-world problems, as demonstrated through impactful internships and entrepreneurial projects.


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Science (BSc) Computer Science} \hfill {September 2021 - June 2024} \\
\textit{University of Bristol} \hfill \textit{Bristol, UK} \\
Graduated with a 2:1 \\
Highlighted units: types and lambda calculus, machine learning (coursework), computer graphics

{\bf A levels} \hfill {September 2016 - June 2021} \\
\textit{Ampleforth College} \hfill \textit{Yorkshire, UK} \\
Further mathematics, mathematics, computer science, physics: A*, A*, A*, A

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILL
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

{\bf Programming Languages:} Python, C\texttt{++}, C, JavaScript, TypeScript \\
{\bf Web Technologies:} HTML \& CSS, React \\
{\bf Tools:} Kubernetes, Docker, Git, LaTeX, CI/CD Pipelines \\
{\bf Languages:} Fluent in English and French

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\textbf{Software Engineering Intern (C\texttt{++})} \hfill June 2023 - August 2023 \\
\textit{FN Herstal}, Herstal, Belgium \\
Designed and implemented a system to calculate the coding-standard-coverage value of a static analysis configuration. It does this by checking the static analyser's output to counter-examples (code snippets) to each rule in the coding standard. This system identified which custom checks should be added to the static analysis configuration, as well as which rules of the coding standard need to be verified by a human during code review. All this information is displayed in an automatically generated web page.

\textbf{Teaching Assistant} \hfill September 2022 - June 2023 \\
\textit{University of Bristol}, Bristol, UK \\
Supported first-year students in 'Imperative Programming' and 'Mathematics B' courses, providing in-class mentoring to improve understanding and performance.

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}
\vspace{-1.25em}

\item \textbf{SPQM Odoo Module: Solar Panel Quote Maker (python, Odoo)}  - \href{https://github.com/ferdinandhubbard981/spqm}{git repo} - \href{http://109.132.176.243:8069/}{demo} \hfill October 2024 - November 2024 \\
Developed a custom Odoo module for a solar panel installation business to streamline quoting. Integrated year-on-year financial projections to showcase ROI of a solar panel installation, improving client conversion rates by 25\%. 

\item \textbf{Odoo tutorial 'estate'} - \href{https://github.com/ferdinandhubbard981/odoo-tutorials}{git repo}\hfill October 2024 \\
Completed the Odoo 'Server framework 101' tutorial, which gave me the ability to make simple Odoo modules, enabling me to start my next project.

\item \textbf{Games Project (rust)} - \href{https://github.com/Team-Yarg/these\_times\_of\_mine}{git repo} \hfill Jan 2024 - May 2024 \\
Worked as part of a team of 7 to develop a game for the Nintendo 3DS in Rust, using a customized Bevy game engine.

\pagebreak

\item \textbf{RecallAI (Kubernetes, python, typescript)} \hfill May 2023 - September 2023 \\
Co-developed a website that generates flashcards from lectures and videos. It leverages existing ML models to generate a transcript, and then condenses that information into flashcards. The app is hosted in a bare-metal k8s instance, and was developed to be horizontally scalable.

\item \textbf{Composite Design Tools (TypeScript, React)} \hfill September 2022 - May 2023 \\
Collaborated with Imperial College London's material science department to create a web-based tool for visualizing and analyzing compressive strength models.

\item \textbf{Pregame Analysis for League of Legends (Python, TensorFlow)} \hfill 2021 \\
Trained a neural network to predict game outcomes based on millions of pre-game data, achieving 70\% accuracy. I also used Bayesian Optimization to tune the neural network's hyper-parameters

\item \textbf{Maths Toolkit (C++, JavaScript)} \hfill 2021 \\
Created an educational toolkit for A-Level students, simplifying complex topics like the Simplex algorithm, matrix operations, and numerical solutions for polynomials.

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Extra-Curricular Activities} 
\vspace{-1.25em}

\item \textbf{Sports:}
Was an active member of the UoB tennis society and represented the University of Bristol in clay pigeon shooting competitions. Passionate about running, golf, and climbing. \\
\vspace{-1.25em}

\item \textbf{Technical Activities:}
Participated in a CTF competition organized by BAE Systems and the Bristol Computer Science Society, solving cybersecurity challenges.

\end{rSection}

\end{document}
